\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-10-21 main.tex
Updates from Overleaf

fig, axes = plt.subplots(2, 2, figsize=(8, 8), constrained_layout=True)
# Create the Devices
ring = make_ring(square=False)
square_ring = make_ring(square=True)
# min_triangles specifies the minimum number of mesh elements.
min_triangles = 12000
# optimesh_steps specifies the the number of iterations of
# optimesh optimization to perform.
# Set optimesh_steps=None to disable optimesh optimization.
optimesh_steps = (None, 40)
# For more meshing options, see the docstring for Device.make_mesh().
for row, device in zip(axes, (ring, square_ring)):
    for ax, opt_steps in zip(row, optimesh_steps):
        # Generate and visualize the mesh
        device.make_mesh(min_triangles=min_triangles, optimesh_steps=opt_steps)
        device.plot_mesh(ax=ax, color="gray", linewidth=0.75)
        device.plot_polygons(ax=ax, linewidth=3, legend=False)
\end{minted}
\captionof{listing}{Generating and visualizing the computational mesh.}
\label{code:mesh_generation}
\end{code}

>>>>

fig, axes = plt.subplots(2, 2, figsize=(6, 6), constrained_layout=True)
# Create the Devices
ring = make_ring(square=False)
square_ring = make_ring(square=True)
# min_triangles specifies the minimum number of mesh elements.
min_triangles = 12000
# optimesh_steps specifies the the number of iterations of
# optimesh optimization to perform.
# Set optimesh_steps=None to disable optimesh optimization.
optimesh_steps = (None, 40)
# For more meshing options, see the docstring for Device.make_mesh().
for row, device in zip(axes, (ring, square_ring)):
    for ax, opt_steps in zip(row, optimesh_steps):
        # Generate and visualize the mesh
        device.make_mesh(min_triangles=min_triangles, optimesh_steps=opt_steps)
        device.plot_mesh(ax=ax, color="gray", linewidth=0.75)
        device.plot_polygons(ax=ax, linewidth=3, legend=False)
\end{minted}
\captionof{listing}{Generating and visualizing the computational mesh.}
\label{code:mesh_generation}
\end{code}
